Looking for a Signal in the Noise: Revisiting Obesity and the microbiome

### 2016-03-23 Sze_ObesityMicrobiomeMetaNoMetaHit_PeerJ_2016.Rmd
Methods revisions to bring in power analysis

In the second strategy, we pooled the relative risk (RR) values for each study. For each study we partitioned the subjects into a low or high group depending on whether their diversity or B/F was below or above the median value for the study. The RR was then calculated as the ratio of the number of obese individuals in the low group to the number of obese individuals in the high group. We then performed a Fisher exact-test to test whether the RR was significantly different from 1.0 using the epiR (v0.9-6.9) and metafor (v1.9-8) packages. Finally, we assessed the potential publication bias in the diversity and B/F analyses using a funnel plot.

@@

>>>>

In the second strategy, we pooled the relative risk (RR) values for each study. For each study we partitioned the subjects into a low or high group depending on whether their diversity or B/F was below or above the median value for the study. The RR was then calculated as the ratio of the number of obese individuals in the low group to the number of obese individuals in the high group. We then performed a Fisher exact-test to test whether the RR was significantly different from 1.0 using the epiR (v0.9-6.9)[@citation] and metafor (v1.9-8)[@citation] packages. Finally, we assessed the potential publication bias in the diversity and B/F analyses using a funnel plot.

@@

We performed power analyses to assess the ability to detect varying effect sizes for the observed study designs. We also predicted the number of individuals required to observe a power of 80% when non-obese and obese individuals were equally represented in the study. Power calculations assumed the data were normally distributed. Since the observed data were not always normally distributed, the observed power is probably overestimated and the number of required subjects is probably underestimated. We used Fisher's exact test to calculate power for relative risk data. **To make comparisons of power calculations across studies meaningful, we assumed the proportion of obese individuals was consistent and used the proportion of obese individuals across all studies.** Power analyses were performed using the statmod [@citation] and pwr [@citation] R packages.
